
Task:
A fire insurance company wants to relate the amount of fire damage in major residential fires to the distance between the burning house and the nearest fire station.
The study is to be conducted in a large suburb of a major city; a sample of 15 recent fires in this suburb is selected. 
The amount of damage, y, and the distance between the fire and the nearest fire station, x, are recorded for each fire.

We assume a simple linear relationship between y and x, and hypothesis that the model is of the following form:
y = β0+ β1x + ε

```{r}
# Use R to estimate the unknown parameters of the hypothesized model. Find the least squares estimates of the slope βˆ1 and intercept βˆ0 on the printout. Write down the least squares equation for this model.
damage <- c(26.2, 17.8, 31.3, 23.1, 27.5, 36.0, 14.1, 22.3, 19.6, 31.3, 24.0, 17.3, 43.2, 36.4, 26.1)
distance <- c(3.4, 1.8, 4.6, 2.3, 3.1, 5.5, 0.7, 3.0, 2.6, 4.3, 2.1, 1.1, 6.1, 4.8, 3.8)
FireDam <- data.frame(damage, distance)
lm.fit <- lm(damage ~ distance, FireDam)
lm.fit
# From the output, βˆ1 = 4.919 and βˆ0 = 10.278. 
# As a result, the least squares equation is: 
# damage = 4.919 ∗ distance + 10.278.
```

```{r}
# Plot the dataset and the least squares line on the same figure.
plot(distance, damage,
xlab ="distance", ylab = "damage", main = "Plot of distance vs damage")
abline(lm.fit)
```

```{r}
# What are the RSE and R-squared values of this model?
summary(lm.fit)
```

```{r}
# Predict the value of damage for a new set of distances (distance = 0.5, 1.5, 2.5, 3.5). 
predict(lm.fit, newdata = data.frame(distance = 0.5:3.5) )
```

```{r}
# Find the confidence interval for the prediction of damage for a new set of distance (distance = 0.5, 3, 5.5).
 predict(lm.fit, data.frame(distance=(c(0.5,3,5.5))), interval="confidence")
```

```{r}
# Find the prediction interval for the prediction of damage for a new set of distance (distance = 0.5, 3, 5.5).
 predict(lm.fit, data.frame(distance=(c(0.5,3,5.5))), interval="prediction")
```

```{r}
# Plot the confidence intervals and prediction intervals in the same figure by using a new set of distance (distance=seq(0.75,6.0,length=51)).
plot(distance, damage,
xlab="distance", ylab = "damage",
main = "Confidence intervals and prediction intervals", ylim = c(10,50))
abline(lm.fit)

newDist <- data.frame(distance=seq(0.75,6.0,length=51))
p_conf <- predict(lm.fit, newDist, interval="confidence")
p_pred <- predict(lm.fit, newDist, interval="prediction") 
lines(newDist$distance, p_conf[,"lwr"], col="red", type="b", pch="+") 
lines(newDist$distance, p_conf[,"upr"], col="red", type="b", pch="+") 
lines(newDist$distance, p_pred[,"upr"], col="blue", type="b", pch="*") 
lines(newDist$distance, p_pred[,"lwr"], col="blue", type="b", pch="*") 
legend("bottomright",
pch=c("+","*"),
 col=c("red","blue"),
legend = c("confidence","prediction"))
```

